---
title: "CCDM"
author:
  - name: Adam Sparks
    orcid: 0000-0002-0061-8359
    email: adam.sparks@curtin.edu.au
params:
  affiliation: CU
date: last-modified
format:
  cbada-revealjs: default
---

```{r}
#| label: load
#| message: false

if (!require(pak)) {
  install.packages("pak", dependencies = TRUE)
}

if (!require(gapminder)) {
  install.packages("gapminder")
}

if (!require(gt)) {
  install.packages("gt")
}

library(ggplot2)
```

## An CCDM Reveal.js Theme for Quarto

This Quarto extension allows you to create your slides using a theme that follows CCDM typography and colour styles and provides the official CCDM logo and cover image for the title slide.

## Basic Tables

```
| Syntax      | Description |
| ----------- | ----------- |
| Header      | Title       |
| Paragraph   | Text        |
```

That renders like this.

  | Syntax    | Description |
  | --------- | ----------- |
  | Header    | Title       |
  | Paragraph | Text        |

## Advanced Tables

```{r}
#| label: CCDM_table
#| message: false
#| echo: true

library(dplyr)
library(gt)

gt <- gt(
  head(airquality) |>
    mutate(`Month Name` = "May")
)
gt
```

::: aside
This is an aside.
:::

## Figures with {ggplot2}

```{r}
#| label: ggplot2-figure
#| message: false

#Prepare data

library(gapminder)
library(dplyr)
library(ggplot2)

facet <- gapminder |>
  filter(continent != "Americas") |>
  group_by(continent, year) |>
  summarise(pop = sum(as.numeric(pop)))

#Make plot
ggplot() +
  geom_area(data = facet, aes(x = year, y = pop, fill = continent)) +
  facet_wrap(~continent, ncol = 5) +
  scale_y_continuous(
    breaks = c(0, 2000000000, 4000000000),
    labels = c(0, "2bn", "4bn")
  ) +
  geom_hline(yintercept = 0, linewidth = 1, colour = "#474747") +
  theme(legend.position = "none", axis.text.x = element_blank()) +
  labs(
    title = "Asia's rapid growth",
    subtitle = "Population growth by continent, 1952-2007"
  )
```

## Slides With Columns

::: columns
::::: {.column width="50%"}
This is a column on the left.
:::::

::::: {.column width="50%"}
This is a column on the right.
:::::
:::

## More Information

You can learn more about controlling the appearance of revealjs output here: <https://quarto.org/docs/presentations/revealjs/>

```{=html}
<!-- Uncomment if you have a bibliography
## References 
-->
```
