---
title: "CCDM"
author: "Centre for Crop and Disease Managment"
date: last-modified
format:
  cbada-pptx: default
---

```{r}
#| label: load
#| message: false

if (!require(pak)) {
  install.packages("pak", dependencies = TRUE)
}
if (!require(flextable)) {
  pak::pak("flextable", dependencies = TRUE)
}

if (!require(gapminder)) {
  pak::pak("gapminder", dependencies = TRUE)
}

if (!require(gt)) {
  pak::pak("gt", dependencies = TRUE)
}

library(ggplot2)
```

## A CCDM pptx Theme for Quarto

This Quarto extension allows you to create your slides using a theme that follows CCDM typography and colour styles and provides the official CCDM logo and cover image for the title slide.

## Bullet point

- Point 1
- Point 2

## Tables

### Example

```{r}
#| label: tab
#| message: false
#| echo: false

library(dplyr)
library(flextable)

# set flextable theme
flex_tab <- flextable(
  head(airquality) |>
    mutate(`Month Name` = "May")
) |>
  autofit()
flex_tab
```

## Figures with {ggplot2}

```{r}
#| label: ggplot2-figure
#| message: false

#Prepare data

library(gapminder)
library(dplyr)
library(ggplot2)

facet <- gapminder |>
  filter(continent != "Americas") |>
  group_by(continent, year) |>
  summarise(pop = sum(as.numeric(pop)))
#> `summarise()` has grouped output by 'continent'. You can override using the
#> `.groups` argument.

#Make plot
ggplot() +
  geom_area(data = facet, aes(x = year, y = pop, fill = continent)) +
  scale_fill_manual(values = col_values) +
  facet_wrap(~continent, ncol = 5) +
  scale_y_continuous(
    breaks = c(0, 2000000000, 4000000000),
    labels = c(0, "2bn", "4bn")
  ) +
  geom_hline(yintercept = 0, linewidth = 1, colour = "#474747") +
  theme(legend.position = "none", axis.text.x = element_blank()) +
  labs(
    title = "Asia's rapid growth",
    subtitle = "Population growth by continent, 1952-2007"
  )
```

## Slides With Columns

::: columns
::::: {.column width="50%"}
This is a column on the left.
:::::

::::: {.column width="50%"}
This is a column on the right.
:::::
:::

# Thank You

```{=html}
<!-- Uncomment if you have a bibliography
## References
-->
```
